Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2024-01-31 supplementary_thev_trxptome.Rmd
finished discussion; improved supp tables

```{r Sup Table 1A}
set_flextable_defaults(font.size = 8)
make_reg_stats_table <- function(tp_table){
  return(tp_table %>%
    select(-junc_freq) %>% 
    flextable() %>% 
    theme_zebra() %>% 
    set_header_labels(timepoint = "Time", region = "Region", strand = "Strand",
                      sum_reads_reg = "Total Reads", perc_reg = "Percentage") %>% 
    flextable::width(width = 0.8) %>% 
    flextable::align(align = "center", part = "all") %>%
    flextable::set_table_properties(layout = "fixed", align = "left",
                       opts_pdf = list(caption_repeat = FALSE),
                       opts_word = list(split = F))
  )
}
make_reg_stats_table(tp_reg_expr_12) %>%
  set_caption("Table 1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")

@@

In the table above, the restriction sites in the primer tails are shown in lowercase letters. All the primer melting temperatures (TMs) are 58-60^o^C using a hot start Taq DNA polymerase. The PCR reaction mix was done per manufacturer's instructions. The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (at least 53^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes. We used 35 cycles of amplification.

>>>>

```{r Sup Table 1A}
set_flextable_defaults(font.size = 8)
make_reg_stats_table <- function(tp_table){
  return(tp_table %>%
    select(-junc_freq) %>% 
    mutate(region = ifelse(is.na(region), "Unassigned", region)) %>% 
    flextable() %>% 
    theme_zebra() %>% 
    set_header_labels(timepoint = "Time", region = "Region", strand = "Strand",
                      sum_reads_reg = "Total Reads", perc_reg = "Percentage") %>% 
    flextable::width(width = 0.8) %>% 
    flextable::align(align = "center", part = "all") %>%
    flextable::set_table_properties(layout = "fixed", align = "left",
                       opts_pdf = list(caption_repeat = FALSE),
                       opts_word = list(split = F))
  )
}
make_reg_stats_table(tp_reg_expr_12) %>%
  set_caption("Table 1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")

@@

In the table above, the restriction sites in the primer tails are shown in lowercase letters. All the primer melting temperatures (TMs) are 58-60^o^C using a hot start Taq DNA polymerase. The PCR reaction mix was done per manufacturer's instructions. The PCR cycling conditions were as follows: Initial denaturation -- 95^o^C for 1 minute; cyclical denaturation -- 95^o^C for 30 seconds, annealing -- variable temperature (53^o^C-56^o^C) for 30 seconds, primer extension -- 68^o^C for variable time, and final elongation -- 68^o^C for 5 minutes. We used 35 cycles of amplification.
